### 2016-09-29 results.tex
working on GBF section

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,\qry_x)$}\\
if $\privaux \neq \emptystring$ then\\
\nudge $M \gets \pubaux$, $K_1,K_2,\ldots,K_k \gets \privaux$\\
else\\
\nudge $M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
$x' \gets 0^\lambda$\\
for $j \in \{1,2,\dots,k\}$\\
\nudge $h_j \gets H_{K_j}(x)$\\
\nudge $x' \gets x' \xor M[h_j]$\\
if $x' =x $ then Return 1\\
Return 0
}
\caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
  filter $\setprim_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times
 \elts \to [m]$. The query set is $\calQ=\{\qry_x\colon
  \univ \to \bits\}$ where $\qry_x(S)=1 \Leftrightarrow x \in S$.}

\end{figure}

@@

\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} secret hash case, \textbf{Right:} public hash case.}
\label{fig:adv-bi-lin-ss}
\end{figure}

>>>>

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,\qry_x)$}\\
if $\privaux \neq \emptystring$ then\\
\nudge $M \gets \pubaux$, $K_1,K_2,\ldots,K_k \gets \privaux$\\
else\\
\nudge $M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
$x' \gets 0^\lambda$\\
for $j \in \{1,2,\dots,k\}$\\
\nudge $h_j \gets H_{K_j}(x)$\\
\nudge $x' \gets x' \xor M[h_j]$\\
if $x' =x $ then Return 1\\
Return 0
}
\caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
  filter $\setprim_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times
 \elts \to [m]$. The query set is $\calQ=\{\qry_x\colon
  \univ \to \bits\}$ where $\qry_x(S)=1 \Leftrightarrow x \in S$.}
\label{fig:gbf}
\end{figure}

@@

\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} secret hash case, \textbf{Right:} public hash case.}
\label{fig:adv-bi-lin-ss}
\end{figure}
\heading{Correctness.}
Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
structure called a \emph{garbled Bloom filter}.  We give the
pseudocode for it in Figure~\ref{fig:gbf}

If the filter and the hash functions are public, there is a naive
attack that works for some interesting parameters.  Pick~$k$ positions
$i_1,i_2,\ldots,i_k$, xor strings at these positions to get a
candidate~$x$.  If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots
\wedge h_k(x) = i_k$ then either $x \in S$ or~$x$ is a
false-positive. (You don't have to do all~$k$ hashes, you can stop as
soon as one fails to match the index.) Say you have a 1000-position
filter ($m=1000$) and a 100-element set ($n=100$), and you are willing
to tolerate a 1\% FP rate.  Then you'd set $k=4$ (a la Squid).  There
are roughly $2^{35}$ subsets of 4 indices to consider, which is
reasonable on a laptop these days.  (Also, since $n=100$ the expected
number of trials is roughly $2^{28}$.) With the FP rate of 1\%, if you
find a winner then almost certainly it is in the set.  Granted, this
attack is naive, but notice that you \emph{cannot} mount it against a
standard Bloom filter. Also notice that this attack might be
significantly more efficient than brute force guessing over the
universe of inputs (imagine that $U=\bits^{64}$), even if you know
that the distribution deviates significantly from uniform.
